---
title: "TUGAS APG Pert 1"
author: "Fatkhul Mukhlish Al-haq"
date: "2/7/2021"
output:
  word_document: default
  html_document: default
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE, comment=NA)
```

## FUNCTION
```{r echo=TRUE}
# Fungsi rata-rata sample
meanSample<- function(x){
  meanS = sum(x, na.rm = TRUE)/length(!is.na(x))
  return(meanS)
}

# Fungsi varians sample
varianceSample<- function(x){
  meanx = meanSample(x)
  diff = x - meanx
  squared_diff = diff^2
  variansS = sum(squared_diff)/ (length(x) - 1)
  return(variansS)
}

# Fungsi Covarians sample
covarianSample<- function(x,y){
  if(length(x)!=length(y)){
    stop('banyak sample x harus sama dengan y')
  }
  x.bar = meanSample(x)
  y.bar = meanSample(y)
  N = length(x)
  
  Cov = (sum((x-x.bar)*(y-y.bar)))/(N-1)
  return(Cov)
}

# Fungsi Correlation sample
correlationSample<- function(x,y){
  cor = covarianSample(x,y)/sqrt(varianceSample(x)*varianceSample(y))
  return(cor)
}

```


## NO 1.1

```{r echo=FALSE, results='asis'}
tabl <- " Consider the seven pairs of measurements (x1 , x2) plotted in Figure 1.1:

                    x1| 3  4    2  6  8   2  5  
                   ---|-------------------------
                    x2| 5  5.5  4  7  10  5  7.5
"
cat(tabl)

```

Calculate the sample means x1 and x2, the sample variances s11 and s22, and the sample covariance s12! 

Jawab:

```{r}
# input data
x1<-c(3,4,2,6,8,2,5)
x2<-c(5,5.5,4,7,10,5,7.5)

# Mean 
meanSample(x1)
meanSample(x2)

# Variance
varianceSample(x1)
varianceSample(x2)

# Covariance
covarianSample(x1,x2)
```

## NO 2

```{r echo=FALSE, results='asis'}
tabl <- "The 10 largest U.S. industrial corporations yield in millions of dollars the following data:

      |     Company      | x1 = sales | x2 = profits | x3 = assets |
      |:----------------:|:----------:|:------------:|:-----------:|
      | General Motors   |  126,974   |    4,224     |   173,297   |
      | Ford             |   96,933   |    3,835     |   160,893   |
      | Exxon            |   86,656   |    3,510     |    83,219   |
      | IBM              |   63,438   |    3,758     |    77,734   |
      | General Electric |   55,264   |    3,939     |   128,344   |
      | Mobil            |   50,976   |    1,809     |    39,080   |
      | Philip Morris    |   39,069   |    2,946     |    38,528   |
      | Chrysler         |   36,156   |      359     |    51,038   |
      | Du Pont          |   35,209   |    2,480     |    34,715   |
      | Texaco           |   32,416   |    2,413     |    25,636   |
"
cat(tabl)
```

a.  Plot the scatter diagram and marginal dot diagrams for variables x1 and x2 . Comment on the appearance of the diagrams. 

b.  Compute x1 , x2 , s1 1 , s22 , s12, and r12. Interpret r12. 

Jawab:

```{r}
# Create Data frame
library(ggplot2)
library(ggExtra)
company<- c('General Motors', 'Ford', 'Exxon', 'IBM', 'General Electric', 'Mobil', 'Philip Morris', 'Chrysler', 'Du Pont', 'Texaco')
sales<- c(126974, 96933, 86656, 63438, 55264, 50976, 39069, 36156, 35209, 32416)
profits<- c(4224, 3835, 3510, 3758, 3939, 1809, 2946, 359, 2480, 2413)
assets<- c(173297, 160893, 83219, 77734, 128344, 39080, 38528, 51038, 34715, 25636)
dataUS<- data.frame(company,sales,profits,assets)

# Scatter plot x1,x2
plotScat<- ggplot(dataUS, aes(x = sales, y = profits)) +
  geom_point() +
  labs(title = "Scatter plot Sales and Profits", x = "Sales in millions of dollars", y = "profits in millions of dollars")

# Marginal plot histogram
plotMargin1<- ggMarginal(plotScat, type = "histogram", size=3, colour ="red")

# Marginal plot density
plotMargin2<- ggMarginal(plotScat, type = "density", size = 3, colour ="red")

# Marginal box plot
plotMargin3 <- ggMarginal(plotScat, type = "boxplot", size = 3)
```

- Scatter Plot x1, x2

```{r echo=FALSE}
plotScat
```

- Marginal Plot Histogram x1,x2

```{r echo=FALSE}
plotMargin1
```

- Marginal Plot Density x1,x2

```{r echo=FALSE}
plotMargin2
```

- Marginal Box Plot x1,x2

```{r echo=FALSE}
plotMargin3
```

- Means

```{r}
#x1
meanSample(dataUS$sales)

#x2
meanSample(dataUS$profits)
```

- Variance

```{r}
#x1
varianceSample(dataUS$sales)
#x2
varianceSample(dataUS$profits)
```

- Covariance x1,x2

```{r}
covarianSample(dataUS$sales,dataUS$profits)
```

- Correlation x1,x2

```{r}
correlationSample(dataUS$sales,dataUS$profits)
```
interpretasi: Berdasarkan hasil korelasi diatas, antara sales dan profits memiliki hubungan positif sebesar 0.676 yang berarti ketika sales bertambah, maka profits juga bertambah.